---
title: "A Maize-Soybean Intercrop Canopy and its Influence on Yield and Water-Use Efficiency."
author: "Elena A. Pelech and Brendan C.S. Alexander"
date: "November 19, 2018"
output:
  pdf_document: default
  word_document: default
subtitle: "Master code document for the project"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the yield data and making boxplots
**Note: Code that starts with a "#" is commented out. It is not meant to be run.**

### Corn and IC corn

This code reads-in the yield data and creates a new dataset (corn.yield) that only has corn and IC observations.
Note that I do create new names for the columns.

There is a linear mixed model fit, however the summary is not displayed.
The model is:
$$\underbrace{y_{ij}}_9=\underbrace{\mu}_1 + \underbrace{\tau_i}_2 + \underbrace{b_j}_2 +\underbrace{\epsilon_{ij}}_4$$

where $y_{ij}$ is the yield of the $i^{th}$ treatment in the $j^{th}$ block, $\tau_i$ is treatment level $i$, $b_j$ is block number $j$, and $\epsilon_{ij}$ is the error for the $i^{th}$ treatment in the $j^{th}$ block.

"ggsave" saves the boxplot as a .png file to wherever your working directory is.

```{r cy, fig.cap="Corn yield comparison between the corn-only treatment plot and the intercropped treatmen in $\\frac{kg}{m^2}$. IC stands for intercrop.",message=FALSE,warning=FALSE}
library(nlme)
library(ggplot2)
library(dplyr)
library(tidyr)
 # import the data
yield <- read.csv("yield.csv")
names(yield) <- c("crop","block","subyield","plot.yield.g","plot.yield.kg","m2.yield.kg","rfr.g","rfr.kg")



corn.yield <- yield%>%
  filter(crop%in%c('corn','ic_corn'))
corn.yield <- droplevels(corn.yield)

corn.yield.fit <- lme(m2.yield.kg~crop,random=~1|block,data = corn.yield)

plot1 <-ggplot(corn.yield,aes(x=crop,y=m2.yield.kg))
plot1 <- plot1+geom_boxplot()
plot1 <- plot1+theme_bw()
plot1 <- plot1+labs(title='Corn yield comparison between the corn-only treatment \n plot and the intercropped treatment.')+
                        xlab('Crop treatment: Corn and intercropped (Corn)')+
                        ylab(expression(paste("Corn yield in ",kg," ", m^{-2})))+
  scale_y_continuous(breaks = pretty(corn.yield$m2.yield.kg,5))
plot1 <- plot1+stat_summary(fun.y=mean, colour="green", geom="point", 
               shape=18, size=3,show.legend = FALSE)
plot1

ggsave("ic_corn.png", device = "png", width = 9, height =5, units = c("in"),dpi = 900)
```

### Soy and IC soy

This code does the same thing, just for soy and IC soy.

```{r sy, fig.cap="Soy yield comparison between the soy-only treatment plot and the intercropped treatment in $\\frac{kg}{m^2}$. IC stands for intercrop.",message=FALSE,warning=FALSE}
soy.yield <- yield%>%
  filter(crop%in%c('soy','ic_soy'))
soy.yield <- droplevels(soy.yield)

soy.yield.fit <- lme(m2.yield.kg~crop,random=~1|block,data = soy.yield)
soy.p <- summary(soy.yield.fit)$tTable[2,5]
plot2 <-ggplot(soy.yield,aes(x=crop,y=m2.yield.kg))
plot2 <- plot2+geom_boxplot()
plot2 <- plot2+theme_bw()
plot2 <- plot2+labs(title='Soy yield comparison between the soy-only \n treatment plot and the intercropped treatment.')+
                        xlab('Crop treatment: Soy and intercropped (Soy)')+
                        ylab(expression(paste("Soy yield in ",kg," ", m^{-2})))+
  scale_y_continuous(breaks = pretty(soy.yield$m2.yield.kg,5))
plot2 <- plot2+stat_summary(fun.y=mean, colour="green", geom="point", 
               shape=18, size=3,show.legend = FALSE)
plot2
ggsave("ic_soy.png", device = "png", width = 9, height =5, units = c("in"),dpi = 900)
```


## Overyielding data manipulation and bootstrap resampling

The "yield" dataset is modified to only include certain columns (select statement), then the data frame is changed from long to wide format (spread statement), and finally I calculate overyielding (mutate statement):

$$oy=\frac{Yield_{ic-corn}}{Yield_{corn}}+\frac{Yield_{ic-soy}}{Yield_{soy}}$$

Note that with only 3 blocks we only have 3 measures for overyielding total.
We have no reason to expect that overyielding will be normally distributed, but just for the hell of it I have an intercept-only model here.
The intercept-only model will estimate the average overyielding and perform a two-sided test to determine if that average (the intercept) is different from zero.

What we really want is to know if the intercept is significantly greater than 1.
A 90% confidence interval will let us essentially do a one sided t-test at $\alpha=0.05$.
(Spoiler: not significant).

```{r}
over.yield <- yield%>%
  select(crop,block,m2.yield.kg)%>%
  spread(key=crop,value=m2.yield.kg)%>%
  mutate(oy=ic_corn/corn+ic_soy/soy)

oy.fit <- lm(oy~1,data=over.yield)
confint(oy.fit,level = 0.9)
```

Because our confidence interval contains values $\leq1$ we reject the alternative hypothesis and conclude that we have no evidence for overyielding.

**Note that the et data frame is being setup here at the same time**

```{r}
# import the data
et <- read.csv('wue.csv')
et <- head(et,-3)
et <- droplevels(et)

et <- et%>%
  #RN
  mutate(rnsw=(rnsw_1+rnsw_2)/2)%>%
  mutate(senssw=(senssw_1+senssw_2)/2)%>%
  mutate(rnlw=(rnlw_1+rnlw_2)/2)%>%
  mutate(senslw=(senslw_1+senslw_2)/2)%>%
  mutate(netsw=rnsw/senssw*1000)%>%
  mutate(netlw=rnlw/senslw*1000)%>%
  mutate(rn=netsw+netlw)%>%
  #G0
  mutate(shfp=(shfp_1+shfp_2+shfp_3+shfp_4)/4)%>%
  mutate(cal=(cal_1+cal_2+cal_3+cal_4)/4)%>%
  mutate(g80=shfp*cal)%>%
  mutate(c=(c_1+c_2+c_3+c_4)/4)%>%
  mutate(dz=(dz_1+dz_2+dz_3+dz_4)/4)%>%
  mutate(dT=(dT_1+dT_2+dT_3+dT_4)/4)%>%
  mutate(dt=(dt_1+dt_2+dt_3+dt_4)/4)%>%
  mutate(g0=g80+c*dz*(dT/dt))%>%
  #H
  mutate(pa=(pa_1+pa_2)/2)%>%
  mutate(cp=(cp_1+cp_2)/2)%>%
  mutate(ttat=(ttat_1+ttat_2)/2)%>%
  mutate(tair=(tair_1+tair_2)/2)%>%
  mutate(ra=(ra_1+ra_2)/2)%>%
  mutate(h=pa*cp*((ttat-tair)/ra))%>%
  mutate(lamet.ave=rn-g0-h)%>%
  mutate(et.ave=lamet.ave/lam*1800)
  
# split timestamp column into smaller components
month_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",1)
day_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",2)
yrtime_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",3)
yr_split <- sapply(strsplit(yrtime_split,split = ' '),"[",1)
time_split <- sapply(strsplit(yrtime_split,split = ' '),"[",2)
t_1 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",1))
t_2 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",2))/60

#create a new dataframe
et1 <- cbind(yr_split,month_split,day_split,time_split,t_1,t_2,et)
```

```{r}
library(gridExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtable)
library(grid)
library(data.table)
et1$block <- as.factor(et1$block)
# dat1$time_split <- as.numeric(as.character(dat1$time_split))

dat1.1 <- et1%>%
  mutate(t=t_1+t_2)%>%#time in hours
  mutate(sec=t*60*60) #time in seconds #cumulative time in seconds

dat1.1 <- data.table(dat1.1)
dat1.1[, seccum := cumsum(dt_1), by=list(treatment, block)]

dat2 <- dat1.1%>%
  mutate(cumdays=seccum*1.1574*10^-5)%>%
  mutate(dayofyear=cumdays+198)%>%
  filter(dayofyear<=250)

dat3 <- dat2%>%
  filter(dayofyear<=250)%>%
  group_by(treatment,block)%>%
  summarise(sum(et.ave))

dat3 <- as.data.frame(dat3)
# dat3 <- dat3[-1,]
names(dat3) <- c('treatment','block','et')
```

```{r over yield bootstrap, fig.cap="Histrogram of 10000 bootstrapped observations for the relative yield of the intercrop treatment. The mean and mean are both approximately 1.1, and the majority of observations indicate overyielding."}
fullyield <- read.csv("yieldfull.csv")

temp.dat <- data.frame(corn=as.numeric(),
                       soy=as.numeric(),
                       ic_soy=as.numeric(),
                       ic_corn=as.numeric())

temp.et <- data.frame(corn.et=as.numeric(),
                       soy.et=as.numeric(),
                       ic.et=as.numeric()) 

oy.boot <- data.frame(overyield=as.numeric())
oy.et.boot <- data.frame(overyield.et=as.numeric(),
                         overyield.corn.et=as.numeric(),
                         overyield.soy.et=as.numeric(),
                         yield.corn.et=as.numeric(),
                         yield.soy.et=as.numeric(),
                         yield.ic.et=as.numeric(),
                         yield.ic.corn.et=as.numeric(),
                         yield.ic.soy.et=as.numeric(),
                         yield.ic.cornonly.et=as.numeric(),
                         yield.ic.rev.cornonly.et=as.numeric())

nrun <- 10000
for (i in 1:nrun){
  for(j in 1:3){
  b <- sample(1:3,1)
  corn <- fullyield%>%
    filter(crop=='corn' & block==b)
  c <- mean(c(sample(x = corn$yield,size = 2,replace = T)))
  
    soy <- fullyield%>%
    filter(crop=='soy' & block==b)
  s <- mean(c(sample(x = soy$yield,size = 2,replace = T)))
  
    ic_corn <- fullyield%>%
    filter(crop=='ic_corn' & block==b)
  ic <- mean(c(sample(x = ic_corn$yield,size = 2,replace = T)))
  
    ic_soy <- fullyield%>%
    filter(crop=='ic_soy' & block==b)
  is <- mean(c(sample(x = ic_soy$yield,size = 2,replace = T)))
  
  corn.et <- dat3%>%
    filter(treatment=='corn' & block==b)
  ic.et <- dat3%>%
    filter(treatment=='ic' & block==b) 
  s.et <- dat3%>%
    filter(treatment=='soy' & block==b) 
  
  temp.dat[j,1] <- c
  temp.dat[j,2] <- s
  temp.dat[j,3] <- is
  temp.dat[j,4] <- ic
  
  temp.et[j,1] <- corn.et[1,3]
  temp.et[j,2] <- s.et[1,3]
  temp.et[j,3] <- ic.et[1,3]
  
  }
  oy <- sum(temp.dat$ic_corn)/sum(temp.dat$corn)+sum(temp.dat$ic_soy)/sum(temp.dat$soy)
  oy.boot[i,1] <- oy
  
  # Ignore these, I was playing around with other ways to visualize the data.
  # I don't think any of our final graphs were made from these mutations
  oy.et <-oy/sum(temp.et$ic.et)-(1/sum(temp.et$corn.et)+1/sum(temp.et$soy.et))/2
  oy.et.boot[i,1] <- oy.et
  oy.et.boot[i,2] <- oy/sum(temp.et$ic.et)-1/sum(temp.et$corn.et)
  oy.et.boot[i,3] <- oy/sum(temp.et$ic.et)-1/sum(temp.et$soy.et)
  oy.et.boot[i,4] <- sum(temp.dat$corn)/sum(temp.et$corn.et)
  oy.et.boot[i,5] <- sum(temp.dat$soy)/sum(temp.et$soy.et)
  oy.et.boot[i,6] <- sum(temp.dat$ic_soy,temp.dat$ic_corn)/sum(temp.et$ic.et)
  oy.et.boot[i,7] <-sum(temp.dat$ic_soy,temp.dat$ic_corn)/sum(temp.et$ic.et)-sum(temp.dat$corn)/sum(temp.et$corn.et)
  oy.et.boot[i,8] <-sum(temp.dat$ic_soy,temp.dat$ic_corn)/sum(temp.et$ic.et)-sum(temp.dat$soy)/sum(temp.et$soy.et)
  oy.et.boot[i,9] <-sum(temp.dat$ic_corn)/sum(temp.et$ic.et)-sum(temp.dat$corn)/sum(temp.et$corn.et)
  oy.et.boot[i,10] <-sum(temp.et$ic.et)/sum(temp.dat$ic_corn)-sum(temp.et$corn.et)/sum(temp.dat$corn)
}
# hist(oy.boot$overyield)

ploth <- ggplot(oy.boot,aes(x=overyield))
ploth <-ploth+ geom_histogram(color="black", fill="white")
ploth <- ploth+theme_bw()
ploth <- ploth+labs(title='Histogram of bootstrapped relative yields for the intercrop treatment.')+
                        xlab('Relative yield')+
                        ylab("Count")
ploth <- ploth+geom_vline(xintercept = 1,size=1,color="green",linetype = "dashed")
ploth

ggsave("ry_hist.png", device = "png", width = 9, height =5, units = c("in"),dpi = 900)
p<- sum(oy.boot$overyield<=1)/nrun
# p
# median(oy.boot$overyield)
# mean(oy.boot$overyield)

```

## ET graphs

ET throughout the summer for each treatment
```{r}
ggplot(data = dat2) +
  aes(x = dayofyear, y = et.ave, color = treatment) +
  geom_point() +
  theme_minimal()
```

Cumulative ET

```{r, fig.cap="ET integrated over the season for each treatent-block combination using Riemann Sums. (ET in $\\frac{kg}{m^2 season}$)"}
dat3$treatment <- factor(dat3$treatment, levels = c("ic","corn","soy"))
plot4 <- ggplot(data=dat3,aes(x=treatment,y = et))
plot4 <- plot4+geom_boxplot()
plot4 <- plot4+theme_bw()
plot4 <- plot4+labs(title='ET integrated over the season for each treatent-block \n combination using Riemann Sums.')+
                        xlab('Crop treatment: Soy, corn, and intercrop')+
                        ylab("cET")+
  scale_y_continuous(breaks = pretty(dat3$et,5))
plot4 <- plot4+stat_summary(fun.y=mean, colour="green", geom="point", 
               shape=18, size=3)
plot4
ggsave("cet.png", device = "png", width = 9, height =5, units = c("in"),dpi = 900)


fit1 <- lme(et~treatment,random=~1|block,dat3)
# levene.test(y = dat3$et,group = dat3$treatment)
```

## Sunny vs cloudy plots

I don't have any comments here yet, but you came up with a lot of this code so I imagine you might not need additional comments here.

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(esquisse)
library(ggthemes)
# 
#  # import the data
dat <- read.csv('wue.csv')
# 
# split timestamp column into smaller components
month_split <- sapply(strsplit(as.character(dat$timestamp),split = '/'),"[",1)
day_split <- sapply(strsplit(as.character(dat$timestamp),split = '/'),"[",2)
yrtime_split <- sapply(strsplit(as.character(dat$timestamp),split = '/'),"[",3)
yr_split <- sapply(strsplit(yrtime_split,split = ' '),"[",1)
time_split <- sapply(strsplit(yrtime_split,split = ' '),"[",2)
t_1 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",1))
t_2 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",2))/60
# 
# #create a new dataframe
dat1 <- cbind(yr_split,month_split,day_split,time_split,t_1,t_2,dat)
dat1$block <- as.factor(dat1$block)
dat1$time_split <- as.numeric(as.character(dat1$time_split))
dat2 <- dat1%>%
mutate(lamet=as.numeric(as.character(lamet)))%>%
mutate(et=lamet/lam*1800)%>%
group_by(treatment,block)%>%
summarise(sum(et))
dat2 <- as.data.frame(dat2)
dat2 <- dat2[-1,]
names(dat2) <- c('treatment','block','et')
# ```{r, fig.cap="ET integrated over the season for each treatent-block combination using Riemann Sums. (ET in mm season^-1"}
ggplot(data = dat2) +
  aes(x = treatment, y = et) +
  geom_boxplot(fill = "#ffffff") +
  labs(x = "Cropping System",
       y = "cET") +
  theme_par()


library(gridExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtable)
library(grid)
library(data.table)
# 
dat1.1 <- dat1%>%
mutate(t=t_1+t_2)%>%#time in hours
mutate(sec=t*60*60)%>% #time in seconds #cumulative time in seconds
mutate(g0_ave=(g0_1+g0_2+g0_3+g0_4)/4)%>%
mutate(rn_ave=(rn_1+rn_2)/2)%>%
mutate(h_ave=(h_1+h_2)/2)
# 
dat1.1 <- data.table(dat1.1)
dat1.1[, seccum := cumsum(dt_1), by=list(treatment, block)]
# 
dat3 <- dat1.1%>%
filter(month_split==9 & day_split==1)
#### lam_ET cloudy ####
ggplot(data = dat3) +
  aes(x = t, y = lamet, color = treatment) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(lambda~"ET"~" "~(W%.%m^2))) +
  theme_par()
#### GO cloudy ####
ggplot(data = dat3) +
  aes(x = t, y = g0_ave, color = treatment) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(G[0]~" "~(W%.%m^2))) +
  theme_par() 
#### H cloudy ####
ggplot(data = dat3) +
  aes(x = t, y = h_ave, color = treatment) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("H"~" "~(W%.%m^2))) +
  theme_par()
#### Rn cloudy ####
ggplot(data = dat3) +
  aes(x = t, y = rn_ave, color = treatment) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(R[n]~" "~(W%.%m^2))) +
  theme_par()

 dat3.1 <- dat1.1%>%
   filter(month_split==8 & day_split==31)
 #### lam_ET sunny ####
 ggplot(data = dat3.1) +
   aes(x = t, y = lamet, color = treatment) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(lambda~"ET "~(W%.%m^2))) +
   theme_par()
 #### Rn sunny ####
 ggplot(data = dat3.1) +
   aes(x = t, y = rn_ave, color = treatment) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(R[n]~" "~(W%.%m^2))) +
   theme_par()
 #### H sunny ####
 ggplot(data = dat3.1) +
   aes(x = t, y = h_ave, color = treatment) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote("H"~" "~(W%.%m^2))) +
   theme_par()
 #### G0 sunny ####
 ggplot(data = dat3.1) +
   aes(x = t, y = g0_ave, color = treatment) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(G[0]~" "~(W%.%m^2))) +
   theme_par()
 
#### Brendan's Addition ####
# import the data
et <- read.csv('wue.csv')
et <- head(et,-3)
et <- droplevels(et)

et <- et%>%
  #RN
  mutate(rnsw=(rnsw_1+rnsw_2)/2)%>%
  mutate(senssw=(senssw_1+senssw_2)/2)%>%
  mutate(rnlw=(rnlw_1+rnlw_2)/2)%>%
  mutate(senslw=(senslw_1+senslw_2)/2)%>%
  mutate(netsw=rnsw/senssw*1000)%>%
  mutate(netlw=rnlw/senslw*1000)%>%
  mutate(rn=netsw+netlw)%>%
  #G0
  mutate(shfp=(shfp_1+shfp_2+shfp_3+shfp_4)/4)%>%
  mutate(cal=(cal_1+cal_2+cal_3+cal_4)/4)%>%
  mutate(g80=shfp*cal)%>%
  mutate(c=(c_1+c_2+c_3+c_4)/4)%>%
  mutate(dz=(dz_1+dz_2+dz_3+dz_4)/4)%>%
  mutate(dT=(dT_1+dT_2+dT_3+dT_4)/4)%>%
  mutate(dt=(dt_1+dt_2+dt_3+dt_4)/4)%>%
  mutate(g0=g80+c*dz*(dT/dt))%>%
  #H
  mutate(pa=(pa_1+pa_2)/2)%>%
  mutate(cp=(cp_1+cp_2)/2)%>%
  mutate(ttat=(ttat_1+ttat_2)/2)%>%
  mutate(tair=(tair_1+tair_2)/2)%>%
  mutate(ra=(ra_1+ra_2)/2)%>%
  mutate(h=pa*cp*((ttat-tair)/ra))%>%
  mutate(lamet.ave=rn-g0-h)%>%
  mutate(et.ave=lamet.ave/lam*1800)
  
# split timestamp column into smaller components
month_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",1)
day_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",2)
yrtime_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",3)
yr_split <- sapply(strsplit(yrtime_split,split = ' '),"[",1)
time_split <- sapply(strsplit(yrtime_split,split = ' '),"[",2)
t_1 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",1))
t_2 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",2))/60

#create a new dataframe
et1 <- cbind(yr_split,month_split,day_split,time_split,t_1,t_2,et)

#### ####

et1$block <- as.factor(et1$block)
# dat1$time_split <- as.numeric(as.character(dat1$time_split))

dat4 <- et1%>%
  mutate(t=t_1+t_2)%>%#time in hours
  mutate(sec=t*60*60) #time in seconds #cumulative time in seconds

dat4 <- data.table(dat4)
dat4[, seccum := cumsum(dt_1), by=list(treatment, block)]

dat5 <- dat4%>%
  mutate(cumdays=seccum/86400)%>% #1.1574*10^-5
  mutate(dayofyear=cumdays+198)%>%
  filter(dayofyear<=250)%>%
  mutate(ind_sun=ifelse(rn>=500,1,0))%>%
  mutate(dayofyear_rounded=floor(dayofyear))

dat_cloudy <- dat5%>%
filter(month_split==9 & day_split==1)

dat_sunny <- dat5%>%
   filter(month_split==8 & day_split==31)
   
dat6_list <- dat5%>%
  filter(time_split=="12:00" & ind_sun==1)%>%
  group_by(dayofyear_rounded)%>%
  summarise(prop_sun=mean(ind_sun))
dat6_list <- as.data.frame(dat6_list)

dat6_list.1 <- as.data.frame(dat6_list)
names(dat6_list.1) <- c("dayofyear_rounded","prop_sun")

dat6_cl_noon <- anti_join(dat5,dat6_list)
dim(dat6_cl_noon)
dat6_su_noon <- semi_join(dat5,dat6_list)
dim(dat6_su_noon)

dat7_table <- dat5%>%
  filter(sec %in% 32400:54000)%>%
  group_by(dayofyear_rounded)%>%
  summarise(prop_sun=mean(ind_sun))

dat7_table <- as.data.frame(dat7_table)
dat7_table30 <- dat7_table%>%
  filter(prop_sun>0.3)

dat7_cl_percent <- anti_join(dat5,dat7_table30)
dim(dat7_cl_percent)
dat7_su_percent <- semi_join(dat5,dat7_table30)
dim(dat7_su_percent)

anti_join(dat7_table30,dat6_list.1,by="dayofyear_rounded")
anti_join(dat6_list.1,dat7_table30,by="dayofyear_rounded")

#### Which days were sunny? ####
# Looks like we could use something like >0.3 or something.
# Notice how the Rn decreases as expected based on moving father away from the summer solstice. Neat!
# Interesting: If proportion criteria set to >0.3 then the total number of sunny days are the same in the dat6 and dat7 arrays
  # The dat6 and dat7 arrays are not identical though, they disagree on 10 days. Other than those 10 days, they agree.
ggplot(data = dat7_table) +
  aes(x = dayofyear_rounded, y = prop_sun) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Day of the year",
       y = bquote("Proportion of measurements between 9am and 3pm that had  "~R[n]~" above 500.")) +
  theme_par()

#### ttat sunny ####

ggplot(data = dat_sunny) +
  aes(x = t, y = ttat, color = treatment) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("ttat")) +
  theme_par()

 dat3.1 <- dat1.1%>%
   filter(month_split==8 & day_split==31)
 
#### ttat cloudy ####
 ggplot(data = dat_cloudy) +
   aes(x = t, y = lamet, color = treatment) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote("ttat")) +
   theme_par()
 
 
 #### Averaged diurnal measures (sunny) (diff, corn-ic) dat 6 (noon Rn)####
 
 dat_diurnal_s6 <- dat6_su_noon %>%
   group_by(treatment, t)%>%
   summarise(H=mean(h),
             lamet = mean(lamet.ave),
             G=mean(g0),
             T=mean(ttat),
             R=mean(rn))

dat_diurnal_s6 <- as.data.frame(dat_diurnal_s6)

dat_di_corn_s6 <- dat_diurnal_s6%>%
  filter(treatment == "corn")

dat_di_ic_s6 <- dat_diurnal_s6%>%
  filter(treatment == "ic")

Hdiff <- data.frame(Hdiff=as.numeric())
etdiff <- data.frame(etdiff=as.numeric())
Gdiff <- data.frame(Gdiff=as.numeric())
Tdiff <- data.frame(Tdiff=as.numeric())
Rdiff <- data.frame(Rdiff=as.numeric())

for (i in 1:nrow(dat_di_corn_s6)){
  Hdiff[i,1] <- dat_di_ic_s6[i,3]-dat_di_corn_s6[i,3]
  etdiff[i,1] <- dat_di_ic_s6[i,4]-dat_di_corn_s6[i,4]
  Gdiff[i,1] <- dat_di_ic_s6[i,5]-dat_di_corn_s6[i,5]
  Tdiff[i,1] <- dat_di_ic_s6[i,6]-dat_di_corn_s6[i,6]
  Rdiff[i,1] <- dat_di_ic_s6[i,7]-dat_di_corn_s6[i,7]
}

time <- dat_di_ic_s6$t
diurnal_graph_data_s6 <- cbind(time,Hdiff,etdiff,Gdiff,Tdiff,Rdiff)


#### H diurnral ####
ggplot(data = diurnal_graph_data_s6) +
  aes(x = time, y = Hdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("H"~" "~(W%.%m^2)),
       title = bquote("H difference (ic - corn, sunny noon Rn)")) +
  theme_par()

#### Rn diurnral ####
ggplot(data = diurnal_graph_data_s6) +
  aes(x = time, y = Rdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(R[n]~" "~(W%.%m^2)),
       title = bquote(R[n]~"differnce (ic - corn, sunny noon Rn)")) +
  theme_par()

 #### lam_ET diurnral ####
 ggplot(data = diurnal_graph_data_s6) +
   aes(x = time, y = etdiff) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(lambda~"ET "~(W%.%m^2)),
        title = bquote(lambda~"ET differnce (ic - corn, sunny noon Rn)")) +
   theme_par()

#### GO diurnral ####
ggplot(data = diurnal_graph_data_s6) +
  aes(x = time, y = Gdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(G[0]~" "~(W%.%m^2)),
       title= bquote(G[0]~"differnce (ic - corn, sunny noon Rn)")) +
  theme_par()

#### ttat diurnral ####

ggplot(data = diurnal_graph_data_s6) +
  aes(x = time, y = Tdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("ttat "~degree*C),
       title= "Canopy temp difference (ic - corn, sunny noon Rn)") +
  theme_par()

 #### Averaged diurnal measures (sunny) (diff, corn-ic) dat 7 (prop Rn)####
 
 dat_diurnal_s7 <- dat7_su_percent %>%
   group_by(treatment, t)%>%
   summarise(H=mean(h),
             lamet = mean(lamet.ave),
             G=mean(g0),
             T=mean(ttat),
             R=mean(rn))

dat_diurnal_s7 <- as.data.frame(dat_diurnal_s7)

dat_di_corn_s7 <- dat_diurnal_s7%>%
  filter(treatment == "corn")

dat_di_ic_s7 <- dat_diurnal_s7%>%
  filter(treatment == "ic")

Hdiff <- data.frame(Hdiff=as.numeric())
etdiff <- data.frame(etdiff=as.numeric())
Gdiff <- data.frame(Gdiff=as.numeric())
Tdiff <- data.frame(Tdiff=as.numeric())
Rdiff <- data.frame(Rdiff=as.numeric())

for (i in 1:nrow(dat_di_corn_s7)){
  Hdiff[i,1] <- dat_di_ic_s7[i,3]-dat_di_corn_s7[i,3]
  etdiff[i,1] <- dat_di_ic_s7[i,4]-dat_di_corn_s7[i,4]
  Gdiff[i,1] <- dat_di_ic_s7[i,5]-dat_di_corn_s7[i,5]
  Tdiff[i,1] <- dat_di_ic_s7[i,6]-dat_di_corn_s7[i,6]
  Rdiff[i,1] <- dat_di_ic_s7[i,7]-dat_di_corn_s7[i,7]
}

time <- dat_di_ic_s7$t
diurnal_graph_data_s7 <- cbind(time,Hdiff,etdiff,Gdiff,Tdiff,Rdiff)


#### H diurnral ####
ggplot(data = diurnal_graph_data_s7) +
  aes(x = time, y = Hdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("H"~" "~(W%.%m^2)),
       title = bquote("H difference (ic - corn, sunny prop 9-3, >0.3)")) +
  theme_par()

#### Rn diurnral ####
ggplot(data = diurnal_graph_data_s7) +
  aes(x = time, y = Rdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(R[n]~" "~(W%.%m^2)),
       title = bquote(R[n]~"differnce (ic - corn, sunny prop 9-3, >0.3)")) +
  theme_par()

 #### lam_ET diurnral ####
 ggplot(data = diurnal_graph_data_s7) +
   aes(x = time, y = etdiff) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(lambda~"ET "~(W%.%m^2)),
        title = bquote(lambda~"ET differnce (ic - corn, sunny prop 9-3, >0.3)")) +
   theme_par()

#### GO diurnral ####
ggplot(data = diurnal_graph_data_s7) +
  aes(x = time, y = Gdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(G[0]~" "~(W%.%m^2)),
       title= bquote(G[0]~"differnce (ic - corn, sunny prop 9-3, >0.3)")) +
  theme_par()

#### ttat diurnral ####

ggplot(data = diurnal_graph_data_s7) +
  aes(x = time, y = Tdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("ttat "~degree*C),
       title= "Canopy temp difference (ic - corn, sunny prop 9-3, >0.3)") +
  theme_par()

#### Averaged diurnal measures (cloudy) (diff, corn-ic) dat 6 (noon Rn)####
 
dat_diurnal_c6 <- dat6_cl_noon %>%
   group_by(treatment, t)%>%
   summarise(H=mean(h),
             lamet = mean(lamet.ave),
             G=mean(g0),
             T=mean(ttat),
             R=mean(rn))

dat_diurnal_c6 <- as.data.frame(dat_diurnal_c6)

dat_di_corn_c6 <- dat_diurnal_c6%>%
  filter(treatment == "corn")

dat_di_ic_c6 <- dat_diurnal_c6%>%
  filter(treatment == "ic")

Hdiff <- data.frame(Hdiff=as.numeric())
etdiff <- data.frame(etdiff=as.numeric())
Gdiff <- data.frame(Gdiff=as.numeric())
Tdiff <- data.frame(Tdiff=as.numeric())
Rdiff <- data.frame(Rdiff=as.numeric())

for (i in 1:nrow(dat_di_corn_c6)){
  Hdiff[i,1] <- dat_di_ic_c6[i,3]-dat_di_corn_c6[i,3]
  etdiff[i,1] <- dat_di_ic_c6[i,4]-dat_di_corn_c6[i,4]
  Gdiff[i,1] <- dat_di_ic_c6[i,5]-dat_di_corn_c6[i,5]
  Tdiff[i,1] <- dat_di_ic_c6[i,6]-dat_di_corn_c6[i,6]
  Rdiff[i,1] <- dat_di_ic_c6[i,7]-dat_di_corn_c6[i,7]
}

time <- dat_di_ic_c6$t
diurnal_graph_data_c6 <- cbind(time,Hdiff,etdiff,Gdiff,Tdiff,Rdiff)


#### H diurnral ####
ggplot(data = diurnal_graph_data_c6) +
  aes(x = time, y = Hdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("H"~" "~(W%.%m^2)),
       title = bquote("H difference (ic - corn, cloudy noon Rn)")) +
  theme_par()

#### Rn diurnral ####
ggplot(data = diurnal_graph_data_c6) +
  aes(x = time, y = Rdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(R[n]~" "~(W%.%m^2)),
       title = bquote(R[n]~"differnce (ic - corn, cloudy noon Rn)")) +
  theme_par()

 #### lam_ET diurnral ####
 ggplot(data = diurnal_graph_data_c6) +
   aes(x = time, y = etdiff) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(lambda~"ET "~(W%.%m^2)),
        title = bquote(lambda~"ET differnce (ic - corn, cloudy noon Rn)")) +
   theme_par()

#### GO diurnral ####
ggplot(data = diurnal_graph_data_c6) +
  aes(x = time, y = Gdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(G[0]~" "~(W%.%m^2)),
       title= bquote(G[0]~"differnce (ic - corn, cloudy noon Rn)")) +
  theme_par()

#### ttat diurnral ####

ggplot(data = diurnal_graph_data_c6) +
  aes(x = time, y = Tdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("ttat "~degree*C),
       title= "Canopy temp difference (ic - corn, cloudy noon Rn)") +
  theme_par()

 #### Averaged diurnal measures (cloudy) (diff, corn-ic) dat 7 (prop Rn)####
 
 dat_diurnal_c7 <- dat7_cl_percent %>%
   group_by(treatment, t)%>%
   summarise(H=mean(h),
             lamet = mean(lamet.ave),
             G=mean(g0),
             T=mean(ttat),
             R=mean(rn))

dat_diurnal_c7 <- as.data.frame(dat_diurnal_c7)

dat_di_corn_c7 <- dat_diurnal_c7%>%
  filter(treatment == "corn")

dat_di_ic_c7 <- dat_diurnal_c7%>%
  filter(treatment == "ic")

Hdiff <- data.frame(Hdiff=as.numeric())
etdiff <- data.frame(etdiff=as.numeric())
Gdiff <- data.frame(Gdiff=as.numeric())
Tdiff <- data.frame(Tdiff=as.numeric())
Rdiff <- data.frame(Rdiff=as.numeric())

for (i in 1:nrow(dat_di_corn_c7)){
  Hdiff[i,1] <- dat_di_ic_c7[i,3]-dat_di_corn_c7[i,3]
  etdiff[i,1] <- dat_di_ic_c7[i,4]-dat_di_corn_c7[i,4]
  Gdiff[i,1] <- dat_di_ic_c7[i,5]-dat_di_corn_c7[i,5]
  Tdiff[i,1] <- dat_di_ic_c7[i,6]-dat_di_corn_c7[i,6]
  Rdiff[i,1] <- dat_di_ic_c7[i,7]-dat_di_corn_c7[i,7]
}

time <- dat_di_ic_c7$t
diurnal_graph_data_c7 <- cbind(time,Hdiff,etdiff,Gdiff,Tdiff,Rdiff)


#### H diurnral ####
ggplot(data = diurnal_graph_data_c7) +
  aes(x = time, y = Hdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("H"~" "~(W%.%m^2)),
       title = bquote("H difference (ic - corn, cloudy prop 9-3, <0.3)")) +
  theme_par()

#### Rn diurnral ####
ggplot(data = diurnal_graph_data_c7) +
  aes(x = time, y = Rdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(R[n]~" "~(W%.%m^2)),
       title = bquote(R[n]~"differnce (ic - corn, cloudy prop 9-3, <0.3)")) +
  theme_par()

 #### lam_ET diurnral ####
 ggplot(data = diurnal_graph_data_c7) +
   aes(x = time, y = etdiff) +
   geom_point() +
   scale_color_brewer(palette = "Greys") +
   labs(x = "Time of Day (Hours)",
        y = bquote(lambda~"ET "~(W%.%m^2)),
        title = bquote(lambda~"ET differnce (ic - corn, cloudy prop 9-3, <0.3)")) +
   theme_par()

#### GO diurnral ####
ggplot(data = diurnal_graph_data_c7) +
  aes(x = time, y = Gdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote(G[0]~" "~(W%.%m^2)),
       title= bquote(G[0]~"differnce (ic - corn, cloudy prop 9-3, <0.3)")) +
  theme_par()

#### ttat diurnral ####

ggplot(data = diurnal_graph_data_c7) +
  aes(x = time, y = Tdiff) +
  geom_point() +
  scale_color_brewer(palette = "Greys") +
  labs(x = "Time of Day (Hours)",
       y = bquote("ttat "~degree*C),
       title= "Canopy temp difference (ic - corn, cloudy prop 9-3, <0.3)") +
  theme_par()
```




## Time series analysis

```{r}
library(dplyr)
library(tidyr)

dat_time_day <- dat2%>%
  filter(dayofyear<=250)%>%
  mutate(dayofyear = signif(dayofyear, digits = 5))%>%
  mutate(dayofyear = as.factor(floor(dayofyear)))%>%
  mutate(id = 
           ifelse(block == "1" & treatment == "corn","1",
           ifelse(block == "2" & treatment == "corn","2",
           ifelse(block == "3" & treatment == "corn","3",
           ifelse(block == "1" & treatment == "ic","4",
           ifelse(block == "2" & treatment == "ic","5",
           ifelse(block == "3" & treatment == "ic","6",
           ifelse(block == "1" & treatment == "soy","7",
           ifelse(block == "2" & treatment == "soy","8","9")))))))))
  # group_by(dayofyear,treatment,block)%>%
  # summarise(cET=sum(et.ave))

dat_sas <- dat_time_day%>%
  select(c("dayofyear","block","treatment","rn","g0","h","lamet.ave","et.ave","t","id","cumdays"))%>%
  group_by(block, treatment, id,t)%>%
  summarise(mean_rn=mean(rn),mean_g0=mean(g0),mean_h=mean(h),mean_lamet=mean(lamet.ave),mean_et=mean(et.ave))#%>%
  # mutate(t = as.factor(t))
  # mutate(day = floor(as.numeric(as.character(dayofyear))))
write.csv(dat_sas, file = "sas_repeated.csv")

dat_sas_rand <- dat_time_day%>%
  select(c("dayofyear","block","treatment","rn","g0","h","lamet.ave","et.ave","t","id","cumdays"))%>%
  mutate(t = as.factor(t))
write.csv(dat_sas_rand, file = "sas_repeated_day_rand.csv")


plot=ggplot(dat_sas,aes(x=t,y=mean_et,group=treatment, color=treatment))
plot=plot+geom_point()
plot=plot+geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), level=0.95)
plot

m2 <- gamm(mean_et ~ s(t, by=treatment, k=-1) + treatment,
           random = list(block=~1),data = dat_sas,
           correlation = corAR1(form = ~ 1|block*id))

m1 <- gamm(mean_et ~ s(t, by=treatment) + treatment,
           random = list(block=~1),data = dat_sas)

m0 = gam(mean_et ~ s(t, by=treatment,k=-1) + treatment,data = dat_sas)

plot(m2$gam, shade = TRUE, pages = 1, scale = 0)


fit_sas = lme(mean_et ~ treatment*t,
              random = ~1|id,
              data=dat_sas,
              correlation = corAR1(form=~1|id))

```


### Average ET by hour



### Daily cET


```{r}
library(dplyr)
library(tidyr)
library(nlme)
library(mgcv)

tmp <- tempfile()
download.file("https://github.com/gavinsimpson/random_code/raw/master/derivFun.R",
              tmp, method = "wget")
source(tmp)
tmp <- tempfile()
download.file("https://github.com/gavinsimpson/random_code/raw/master/tsDiagGamm.R",
              tmp, method = "wget")
source(tmp)





m <- gam(lamet.ave ~ treatment + s(t, by = treatment), data = dat_time_sas)
summary(m)
plot(m, residuals = TRUE, pch = 19, cex = 0.75)

# Include the variable "id" instead of "treatment*block"
# Include block
m2 <- gamm(lamet.ave ~ treatment + s(cumdays, by = treatment), data = dat_time_day, correlation = corAR1(form = ~ cumdays|id))
```

