---
title: "Time Series analysis of ET data"
author: "Brendan Alexander"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
```

# Overview


ough explanation into my modeling decisions is given in a file called "time_series.pdf".

There are 3 major sections (copying the 2003 Bernacchi paper):

1. Single day: cloudy vs sunny fits and graphs for $R_n$, $H$, $G_0$, and $\lambda ET$.
2. Averaged diurnal differences between treatments (currently just Corn-IC).
3. Daily $\lambda ET$ graph using total $\lambda ET$ between 11AM and 1PM for Corn, soy and IC.

# Model fits

A typical repeated measures model has the form (using terminology and df specific to a single day of this experiment):

$$\underbrace{y}_{432} = \underbrace{\mu}_{1} + \underbrace{C_i}_{2} + \underbrace{p_{(i)j}}_{6} + \underbrace{T_k}_{47} + \underbrace{CT_{ik}}_{94} + \underbrace{\epsilon_{ijk}}_{282}$$

where $C_i$ it the $i^{th}$ level of crop, $p_{(i)j}$ represents individual plots (analogous to subjects), $T_k$ is the time effect (categorical in our case, unless we want to do a high-order polynomial model or GAM), $CT_{ik}$ is the interaction between crop and time, and $\epsilon_{ijk}$ is the error assumed to be $N\sim (0,\sigma^2)$.

This experiment also has a blocking effect, and I think the correct modification to the model formula is:

$$\underbrace{y}_{432} = \underbrace{\mu}_{1} + \underbrace{b_i}_{2} + \underbrace{C_j}_{2} + \underbrace{\epsilon_{ij}}_{4} + \underbrace{T_k}_{47} + \underbrace{CT_{jk}}_{94} + \underbrace{\epsilon_{ijk}}_{282}$$

where $b_i$ is the blocking effect.
Both equations have effectively two error terms (in the first equation $p_{(i)j}$ is effectively an error term for $C_i$, these models are constructed similarly to split-plots).
Notice that including the blocking effect takes 2 df from $\epsilon_{ij}$ and has no effect on $\epsilon_{ijk}$.

This data also seems to have heterogeneous variance based on time of day as well as treatment.
We solve this issue by including a `weight = ` statement.

For the repeated measures we will include a `correlation = ` statement to allow for time correlation (probably `AR(1)`, but multiple structures have been tried).

A `control = ` statement is included to allow for increased iterations (the complicated analyses need a few more runs to converge than normal).


# Single Day analyses (fig 2 from Bernacchi 2003)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(esquisse)
library(ggthemes)
library(gridExtra)
library(tidyverse)
library(gtable)
library(grid)
library(data.table)
library(nlme)
library(emmeans)
# 
et <- read.csv('wue.csv')
et <- head(et,-3)
et <- droplevels(et)

et <- et%>%
  #RN
  mutate(rnsw=(rnsw_1+rnsw_2)/2)%>%
  mutate(senssw=(senssw_1+senssw_2)/2)%>%
  mutate(rnlw=(rnlw_1+rnlw_2)/2)%>%
  mutate(senslw=(senslw_1+senslw_2)/2)%>%
  mutate(netsw=rnsw/senssw*1000)%>%
  mutate(netlw=rnlw/senslw*1000)%>%
  mutate(rn=netsw+netlw)%>%
  #G0
  mutate(shfp=(shfp_1+shfp_2+shfp_3+shfp_4)/4)%>%
  mutate(cal=(cal_1+cal_2+cal_3+cal_4)/4)%>%
  mutate(g80=shfp*cal)%>%
  mutate(c=(c_1+c_2+c_3+c_4)/4)%>%
  mutate(dz=(dz_1+dz_2+dz_3+dz_4)/4)%>%
  mutate(dT=(dT_1+dT_2+dT_3+dT_4)/4)%>%
  mutate(dt=(dt_1+dt_2+dt_3+dt_4)/4)%>%
  mutate(g0=g80+c*dz*(dT/dt))%>%
  #H
  mutate(pa=(pa_1+pa_2)/2)%>%
  mutate(cp=(cp_1+cp_2)/2)%>%
  mutate(ttat=(ttat_1+ttat_2)/2)%>%
  mutate(tair=(tair_1+tair_2)/2)%>%
  mutate(ra=(ra_1+ra_2)/2)%>%
  mutate(h=pa*cp*((ttat-tair)/ra))%>%
  mutate(lamet.ave=rn-h)%>% # g0 has been removed from the calculation of lamET due to sensor malfunctions
  mutate(et.ave=lamet.ave/lam*1800)
  
# split timestamp column into smaller components
month_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",1)
day_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",2)
yrtime_split <- sapply(strsplit(as.character(et$timestamp),split = '/'),"[",3)
yr_split <- sapply(strsplit(yrtime_split,split = ' '),"[",1)
time_split <- sapply(strsplit(yrtime_split,split = ' '),"[",2)
t_1 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",1))
t_2 <- as.numeric(sapply(strsplit(time_split,split = ':'),"[",2))/60

#create a new dataframe
et1 <- cbind(yr_split,month_split,day_split,time_split,t_1,t_2,et)

et1$block <- as.factor(et1$block)
# dat1$time_split <- as.numeric(as.character(dat1$time_split))

dat1.1 <- et1%>%
  mutate(t=t_1+t_2)%>%#time in hours
  mutate(sec=t*60*60) #time in seconds #cumulative time in seconds

dat1.1 <- data.table(dat1.1)
dat1.1[, seccum := cumsum(dt_1), by=list(treatment, block)]

dat2 <- dat1.1%>%
  mutate(cumdays=seccum*1.1574*10^-5)%>%
  mutate(dayofyear=cumdays+198)%>%
  filter(dayofyear<=250)

# This filters out a lot of September data, readings were erratic in September
# This also creates the subject level tag for each plot (id)
# We create the t-fac variable here (it's just time as a categorical variable)


dat_time_day <- dat2%>%
  filter(dayofyear<=250)%>%
  mutate(dayofyear = signif(dayofyear, digits = 5))%>%
  mutate(dayofyear = as.factor(floor(dayofyear)))%>%
  mutate(id = 
           ifelse(block == "1" & treatment == "corn","1",
           ifelse(block == "2" & treatment == "corn","2",
           ifelse(block == "3" & treatment == "corn","3",
           ifelse(block == "1" & treatment == "ic","4",
           ifelse(block == "2" & treatment == "ic","5",
           ifelse(block == "3" & treatment == "ic","6",
           ifelse(block == "1" & treatment == "soy","7",
           ifelse(block == "2" & treatment == "soy","8","9")))))))))%>%
  mutate(t_fac = as.factor(t))%>%
  mutate(plot = 
           ifelse(block == "1" & treatment == "corn","1",
           ifelse(block == "2" & treatment == "corn","2",
           ifelse(block == "3" & treatment == "corn","3",
           ifelse(block == "1" & treatment == "ic","3",
           ifelse(block == "2" & treatment == "ic","1",
           ifelse(block == "3" & treatment == "ic","2",
           ifelse(block == "1" & treatment == "soy","2",
           ifelse(block == "2" & treatment == "soy","3","1")))))))))%>%
  mutate(plot=as.factor(plot))%>%
  mutate(trt_time = paste0(treatment,t_fac))

# Getting rid of many columns we no longer need...

dat_time_day_reduced = dat_time_day%>%
  select(c("dayofyear","month_split","day_split", "block","treatment","rn","g0","h","lamet.ave","et.ave","t","id","cumdays", "t_fac","plot","trt_time"))

# dat_averaged <- dat_time_day%>%
#   select(c("dayofyear","block","treatment","rn","g0","h","lamet.ave","et.ave","t","id","cumdays", "t_fac","plot"))%>%
#   group_by(block, treatment, id,t,t_fac, plot,trt_time)%>%
#   summarize(mean_rn=mean(rn),mean_g0=mean(g0),mean_h=mean(h),mean_lamet=mean(lamet.ave),mean_et=mean(et.ave))

```


Here's where you can see the days that are currently selected as "sunny" and "cloudy".
Change them as you like using the *time_series_master.rmd* document.

The models here run for September 8th and August 31st.
Changing the date will likely result in the models not running correctly.
There could always be nuissance issues that arise on different days that the model wasn't built for.
Outlying blocks or observations can cause excessive variability, and that causes the variability components to be poorly estimated, resulting in poor residual graphs.
I wouldn't expect any major differences day to day in general though, just graph the data and check to make sure if anything seems a little off on a particular day.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# fit_sas0 is the most similar to sas so far
ctrl <- lmeControl(maxIter = 5000, msMaxIter = 5000, iter.max = 10000,opt='optim')
# , opt='optim'
```



```{r}
dat_cloudy <- dat_time_day_reduced%>%
  filter(month_split==9 & day_split==1) # Change the month and day here

write.csv(dat_cloudy, file = "sas_cloudy.csv")


dat_sunny <- dat_time_day_reduced%>%
  filter(month_split==8 & day_split==31) # Change the month and day here

write.csv(dat_sunny, file = "sas_sunny.csv")

```

## Issues with the data

1. $R_n$ is not replicated over treatments so we can't run a model with treatment as a variable.
We could run a model that estimates $R_n$ wihtout treatment as a variable if we want to use a "global" estimate for $\lambda ET$ calculations.
In Bernacchi (2003) it doesn't seem like $R_n$ has much variability to begin with, so I think it probably doesn't matter.

2. $G_0$ is replicated, but in an incomplete block design (IC in blocks 1,3; Corn in blocks 1,2; Soy in blocks 2,3).
Including block as a random variable might make complicated models harder to run.
We can always drop block as an effect for $G_0$ models and have $n=2$.

Additionally, $G_0$ measurements seem to have maximum and minimum "caps"

```{r, fig.cap="G0 on August 31st. Unexpected cap?"}
ggplot(dat_sunny) +
 aes(x = t, y = g0, colour = block) +
 geom_point(size = 1L) +
 scale_color_hue() +
 theme_minimal() +
 facet_wrap(vars(treatment))
```


3. Some `block*treatment` combinations behave oddly on some days.
It doesn't seem to always be the same combinations.

Example issue with blocks:
Notice that the third block for soy seems to be a major outlier.

It doesn't seem like it's always the same treatment or block, it's day dependent.

```{r, fig.cap="H on August 31st. Notice that the third block for soy seems to be a major outlier (bug on the sensor that day?)."}
ggplot(dat_sunny) +
 aes(x = t, y = h, colour = block) +
 geom_point(size = 1L) +
 scale_color_hue() +
 theme_minimal() +
 facet_wrap(vars(treatment))
```

\pagebreak

## Sunny

### $\lambda ET$

Models are run in the following order.
This was exploratory, and the models are present only for sunny $\lambda Et$ as a talking point about model construction.

1. `fit_sunny_et_0.1` Basic mixed model:
    
    `random = ~1|block/id`
2. `fit_sunny_et_0.2` Unequal variance per time point added to `fit_sunny_et_0.1`: 
    
    `weights = varIdent(form= ~ 1 | t_fac)`
3. `fit_sunny_et_0.3` Unequal variance for treatment added to `fit_sunny_et_0.1`: 
    
    `weights = varIdent(form= ~ 1 | treatment)`
4. `fit_sunny_et_0.4` Unequal variances allowed per time point and per treatment to `fit_sunny_et_0.1`: 
    
    `weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac))` 
5. `fit_sunny_et_full` Adds `AR(1)` correlation structure to `fit_sunny_et_0.4`: 
    
    `correlation = corAR1()`



```{r, cache=T}
dat_sunny_et = dat_sunny%>%
  filter(id !=9) #this corresponds to soy block 3, which is really borked on this day (adds a silly amount of variability, unlike block 1 and 2)
dat_sunny_et = as.data.frame(dat_sunny_et)
dat_sunny_et =droplevels(dat_sunny_et)

fit_sunny_et_0.1 = lme(lamet.ave ~ treatment*t_fac,
              random = ~1|block/id,
              data=dat_sunny_et)



# Weight by time
fit_sunny_et_0.2 = lme(lamet.ave ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | t_fac),
              random = ~1|block/id,
              data=dat_sunny_et)

# Weight by treatment
fit_sunny_et_0.3 = lme(lamet.ave ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | treatment),
              random = ~1|block/id,
              data=dat_sunny_et)

# Weight by both

fit_sunny_et_0.4 = lme(lamet.ave ~ treatment*t_fac,
              weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
              random = ~1|block/id,
              control = ctrl,
              data=dat_sunny_et)


# add ar(1)
fit_sunny_et_full = lme(lamet.ave ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corAR1(),
            control = ctrl,
            data=dat_sunny_et)

# 
```

```{r}
dat_sunny_et_0.1_res = dat_sunny_et%>%
  mutate(res=residuals(fit_sunny_et_0.1, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_et_0.1))

dat_sunny_et_0.2_res = dat_sunny_et%>%
  mutate(res=residuals(fit_sunny_et_0.2, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_et_0.2))

dat_sunny_et_0.3_res = dat_sunny_et%>%
  mutate(res=residuals(fit_sunny_et_0.3, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_et_0.3))

dat_sunny_et_0.4_res = dat_sunny_et%>%
  mutate(res=residuals(fit_sunny_et_0.4, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_et_0.4))


dat_sunny_et_full_res = dat_sunny_et%>%
  mutate(res=residuals(fit_sunny_et_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_et_full))  


plot0.1 = ggplot(data=dat_sunny_et_0.1_res, aes(x=t, y=res, color=treatment))
plot0.1 = plot0.1 + geom_point() + ggtitle("Lamet model 0.1 (Basic)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot0.1 = plot0.1 + scale_x_continuous(breaks=seq(0,24,1))
plot0.1
hist(residuals(fit_sunny_et_0.1, type="normalized"))

plot0.2 = ggplot(data=dat_sunny_et_0.2_res, aes(x=t, y=res, color=treatment))
plot0.2 = plot0.2 +geom_point() + ggtitle("Lamet model 0.2 (Unequal variance by time point)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot0.2 = plot0.2 + scale_x_continuous(breaks=seq(0,24,1))
plot0.2
hist(residuals(fit_sunny_et_0.2, type="normalized"))

plot0.3 = ggplot(data=dat_sunny_et_0.3_res, aes(x=t, y=res, color=treatment))
plot0.3 = plot0.3 +geom_point() + ggtitle("Lamet model 0.3 (Unequal variance by treatment)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot0.3 = plot0.3 + scale_x_continuous(breaks=seq(0,24,1))
plot0.3
hist(residuals(fit_sunny_et_0.3, type="normalized"))

plot0.4 = ggplot(data=dat_sunny_et_0.4_res, aes(x=t, y=res, color=treatment))
plot0.4 = plot0.4 +geom_point() + ggtitle("Lamet model 0.4 (Unequal variance by treatment and time point)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot0.4 = plot0.4 + scale_x_continuous(breaks=seq(0,24,1))
plot0.4
hist(residuals(fit_sunny_et_0.4, type="normalized"))


plot_sunny_full = ggplot(data=dat_sunny_et_full_res, aes(x=t, y=res, color=treatment))
plot_sunny_full = plot_sunny_full +geom_point() + ggtitle("Lamet sunny model Full (unequal variance and AR(1))") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_sunny_full = plot_sunny_full + scale_x_continuous(breaks=seq(0,24,1))
plot_sunny_full
hist(residuals(fit_sunny_et_full, type="normalized"))
qqnorm(residuals(fit_sunny_et_full, type="normalized"))
qqline(residuals(fit_sunny_et_full, type="normalized"))

AIC(fit_sunny_et_0.1)
AIC(fit_sunny_et_0.2)
AIC(fit_sunny_et_0.3)
AIC(fit_sunny_et_0.4)
AIC(fit_sunny_et_full)
```

```{r, fig.cap="Sunny day lamet estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_lamet = as.data.frame(emmeans(fit_sunny_et_full, ~ treatment*t_fac))
means_lamet$t_fac = as.numeric(as.character(means_lamet$t_fac))

plot_lamet = ggplot(data=means_lamet, aes(x=t_fac, y=emmean, color=treatment))
plot_lamet = plot_lamet + geom_point() + xlab("Time Point (Hour)") + ylab("Lamet")
plot_lamet = plot_lamet + scale_x_continuous(breaks=seq(0,24,1))
plot_lamet = plot_lamet + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_lamet
```

\pagebreak

### H

```{r,eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}

dat_sunny_h = dat_sunny%>%
  filter(id !=9)
dat_sunny_h = as.data.frame(dat_sunny_h)


fit_sunny_H_0.1 = lme(h ~ treatment*t_fac,
              random = ~1|block/id,
              data=dat_sunny)



# Weight by time
fit_sunny_H_0.2 = lme(h ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | t_fac),
              random = ~1|block/id,
              data=dat_sunny)

# Weight by treatment
fit_sunny_H_0.3 = lme(h ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | treatment),
              random = ~1|block/id,
              data=dat_sunny)

# Weight by both

fit_sunny_H_0.4 = lme(h ~ treatment*t_fac,
              weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
              random = ~1|block/id,
              data=dat_sunny)


# add ar(1)
fit_sunny_H_full = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny)

fit_sunny_H_full_int = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varIdent(form= ~ 1 | trt_time),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny)

fit_sunny_H_full_int_full = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac),varIdent(form= ~ 1 | trt_time)),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny)



fit_sunny_H_full_test = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny_h)

fit_sunny_H_full_int_test = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varIdent(form= ~ 1 | trt_time),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny_h)

#            
dat_sunny_H_0.1_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny0.1, type="normalized"))%>%
  mutate(pred=predict(fit_sunny0.1))

dat_sunny_H_0.2_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_0.2, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_0.2))

dat_sunny_H_0.3_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_0.3, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_0.3))

dat_sunny_H_0.4_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_0.4, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_0.4))


dat_sunny_H_full_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full))

dat_sunny_H_full_int_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_full_int, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full_int))

dat_sunny_H_full_int_full_res = dat_sunny%>%
  mutate(res=residuals(fit_sunny_H_full_int_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full_int_full)) 

## tests with new dataframe

dat_sunny_H_full_test_res = dat_sunny_h%>%
  mutate(res=residuals(fit_sunny_H_full_test, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full_test))

dat_sunny_H_full_int_test_res = dat_sunny_h%>%
  mutate(res=residuals(fit_sunny_H_full_int_test, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full_int_test))



plot0.1 = ggplot(data=dat_sunny_H_0.1_res, aes(x=t_fac, y=res, color=treatment))
plot0.1 = plot0.1 +geom_point()
plot0.1
hist(residuals(fit_sunny_H_0.1, type="normalized"))

plot0.2 = ggplot(data=dat_sunny_H_0.2_res, aes(x=t_fac, y=res, color=treatment))
plot0.2 = plot0.2 +geom_point()
plot0.2
hist(residuals(fit_sunny_H_0.2, type="normalized"))

plot0.3 = ggplot(data=dat_sunny_H_0.3_res, aes(x=t_fac, y=res, color=treatment))
plot0.3 = plot0.3 +geom_point()
plot0.3
hist(residuals(fit_sunny_H_0.3, type="normalized"))

plot0.4 = ggplot(data=dat_sunny_H_0.4_res, aes(x=t_fac, y=res, color=treatment))
plot0.4 = plot0.4 +geom_point()
plot0.4
hist(residuals(fit_sunny_H_0.4, type="normalized"))


plot_sunny_full = ggplot(data=dat_sunny_H_full_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full = plot_sunny_full +geom_point()
plot_sunny_full
hist(residuals(fit_sunny_H_full, type="normalized"))
qqnorm(residuals(fit_sunny_H_full, type="normalized"))
qqline(residuals(fit_sunny_H_full, type="normalized"))

plot_sunny_full_int = ggplot(data=dat_sunny_H_full_int_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full_int = plot_sunny_full_int +geom_point()
plot_sunny_full_int
hist(residuals(fit_sunny_H_full_int, type="normalized"))
qqnorm(residuals(fit_sunny_H_full_int, type="normalized"))
qqline(residuals(fit_sunny_H_full_int, type="normalized"))

plot_sunny_full_int_full = ggplot(data=dat_sunny_H_full_int_full_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full_int_full = plot_sunny_full_int_full +geom_point()
plot_sunny_full_int_full
hist(residuals(fit_sunny_H_full_int_full, type="normalized"))
qqnorm(residuals(fit_sunny_H_full_int_full, type="normalized"))
qqline(residuals(fit_sunny_H_full_int_full, type="normalized"))

## tests

## this is the best fit by far, removed the offending 
plot_sunny_full_test = ggplot(data=dat_sunny_H_full_test_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full_test = plot_sunny_full_test +geom_point()
plot_sunny_full_test
hist(residuals(fit_sunny_H_full_test, type="normalized"))
qqnorm(residuals(fit_sunny_H_full_test, type="normalized"))
qqline(residuals(fit_sunny_H_full_test, type="normalized"))
###


plot_sunny_full_int_test = ggplot(data=dat_sunny_H_full_int_test_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full_int_test = plot_sunny_full_int_test +geom_point()
plot_sunny_full_int_test
hist(residuals(fit_sunny_H_full_int_test, type="normalized"))
qqnorm(residuals(fit_sunny_H_full_int_test, type="normalized"))
qqline(residuals(fit_sunny_H_full_int_test, type="normalized"))
```

```{r, cache=T}
dat_sunny_h = dat_sunny%>%
  filter(id !=9)
dat_sunny_h = as.data.frame(dat_sunny_h)


fit_sunny_H_full = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_sunny_h)
```

```{r}
dat_sunny_H_full_res = dat_sunny_h%>%
  mutate(res=residuals(fit_sunny_H_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_H_full))

plot_sunny_full = ggplot(data=dat_sunny_H_full_res, aes(x=t, y=res, color=treatment))
plot_sunny_full = plot_sunny_full +geom_point()+ ggtitle("Normalized residuals (H sunny full model)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_sunny_full = plot_sunny_full + scale_x_continuous(breaks=seq(0,24,1))
plot_sunny_full
hist(residuals(fit_sunny_H_full, type="normalized"))
qqnorm(residuals(fit_sunny_H_full, type="normalized"))
qqline(residuals(fit_sunny_H_full, type="normalized"))
```


```{r, fig.cap="Sunny day H estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_h = as.data.frame(emmeans(fit_sunny_H_full, ~ treatment*t_fac))
means_h$t_fac = as.numeric(as.character(means_h$t_fac))

plot_h = ggplot(data=means_h, aes(x=t_fac, y=emmean, color=treatment))
plot_h = plot_h + geom_point()+ xlab("Time Point (Hour)") + ylab("H")
plot_h = plot_h + scale_x_continuous(breaks=seq(0,24,1))
plot_h = plot_h + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_h
```

\pagebreak

### $G_0$

```{r,eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
dat_sunny_g0 = dat_sunny%>%
  filter(id %in% c(1, 2, 4, 6, 8, 9))
dat_sunny_g0 = as.data.frame(dat_sunny_g0)

fit_sunny_G0_0.1 = lme(g0 ~ treatment*t_fac,
              random = ~1|block/id,
              control = ctrl,
              data=dat_sunny_g0)



# Weight by time
fit_sunny_G0_0.2 = lme(g0 ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | t_fac),
              random = ~1|block/id,
              control = ctrl,
              data=dat_sunny_g0)

# Weight by treatment
fit_sunny_G0_0.3 = lme(g0 ~ treatment*t_fac,
              weights = varIdent(form= ~ 1 | treatment),
              random = ~1|block/id,
              control = ctrl,
              data=dat_sunny_g0)

# Weight by both

fit_sunny_G0_0.4 = lme(g0 ~ treatment*t_fac,
              weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
              random = ~1|block/id,
              control = ctrl,
              data=dat_sunny_g0)


# add ar(1)
fit_sunny_G0_full = lme(g0 ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corAR1(),
            control = ctrl,
            data=dat_sunny_g0)

# # add treatment*time weight (doesn't run)
# fit_sunny_G0_full_int = lme(g0 ~ treatment*t_fac,
#             random = ~ 1 | id,
#             weights = varIdent(form= ~ 1 | trt_time),
#             correlation = corARMA(p=1),
#             control = ctrl,
#             data=dat_sunny_g0)
# 
# fit_sunny_G0_full_int_full = lme(g0 ~ treatment*t_fac,
#             random = ~ 1 | block/id,
#             weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac),varIdent(form= ~ 1 | trt_time)),
#             correlation = corARMA(p=1),
#             control = ctrl,
#             data=dat_sunny)



#            
dat_sunny_G0_0.1_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_0.1, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_0.1))

dat_sunny_G0_0.2_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_0.2, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_0.2))

dat_sunny_G0_0.3_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_0.3, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_0.3))

dat_sunny_G0_0.4_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_0.4, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_0.4))


dat_sunny_G0_full_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_full))  


plot0.1 = ggplot(data=dat_sunny_G0_0.1_res, aes(x=t_fac, y=res, color=treatment))
plot0.1 = plot0.1 +geom_point()
plot0.1
hist(residuals(fit_sunny_G0_0.1, type="normalized"))

plot0.2 = ggplot(data=dat_sunny_G0_0.2_res, aes(x=t_fac, y=res, color=treatment))
plot0.2 = plot0.2 +geom_point()
plot0.2
hist(residuals(fit_sunny_G0_0.2, type="normalized"))

plot0.3 = ggplot(data=dat_sunny_G0_0.3_res, aes(x=t_fac, y=res, color=treatment))
plot0.3 = plot0.3 +geom_point()
plot0.3
hist(residuals(fit_sunny_G0_0.3, type="normalized"))

plot0.4 = ggplot(data=dat_sunny_G0_0.4_res, aes(x=t_fac, y=res, color=treatment))
plot0.4 = plot0.4 +geom_point()
plot0.4
hist(residuals(fit_sunny_G0_0.4, type="normalized"))


plot_sunny_full = ggplot(data=dat_sunny_G0_full_res, aes(x=t_fac, y=res, color=treatment))
plot_sunny_full = plot_sunny_full +geom_point()
plot_sunny_full
hist(residuals(fit_sunny_G0_full, type="normalized"))
qqnorm(residuals(fit_sunny_G0_full, type="normalized"))
qqline(residuals(fit_sunny_G0_full, type="normalized"))
```


```{r, cache=T}
dat_sunny_g0 = dat_sunny%>%
  filter(id %in% c(1, 2, 4, 6, 8, 9))
dat_sunny_g0 = as.data.frame(dat_sunny_g0)

fit_sunny_G0_full = lme(g0 ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corAR1(),
            control = ctrl,
            data=dat_sunny_g0)
```

```{r}
dat_sunny_G0_full_res = dat_sunny_g0%>%
  mutate(res=residuals(fit_sunny_G0_full, type="normalized"))%>%
  mutate(pred=predict(fit_sunny_G0_full))  

plot_sunny_full = ggplot(data=dat_sunny_G0_full_res, aes(x=t, y=res, color=treatment))
plot_sunny_full = plot_sunny_full +geom_point()+geom_point()+ ggtitle("Normalized residuals (G0 sunny full model)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_sunny_full = plot_sunny_full + scale_x_continuous(breaks=seq(0,24,1))
plot_sunny_full
hist(residuals(fit_sunny_G0_full, type="normalized"))
qqnorm(residuals(fit_sunny_G0_full, type="normalized"))
qqline(residuals(fit_sunny_G0_full, type="normalized"))
```


```{r, fig.cap= "Sunny day G0 estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_g0 = as.data.frame(emmeans(fit_sunny_G0_full, ~ treatment*t_fac))
means_g0$t_fac = as.numeric(as.character(means_g0$t_fac))


plot_g0 = ggplot(data=means_g0, aes(x=t_fac, y=emmean, color=treatment))
plot_g0 = plot_g0 + geom_point()+ xlab("Time Point (Hour)") + ylab("G0")
plot_g0 = plot_g0 + scale_x_continuous(breaks=seq(0,24,1))
plot_g0 = plot_g0 + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_g0
```

\pagebreak

### $R_n$

$R_n$ isn't replicated over by treatment, there are no statistics required here.

```{r}
ggplot(dat_sunny) +
 aes(x = t, y = rn, colour = treatment) +
 geom_point(size = 1L) +
 scale_color_hue() +
 theme_minimal()
```


\pagebreak

## Cloudy

### $\lambda ET$

```{r, cache=T}
dat_cloudy_et = dat_cloudy#%>%
  # filter(id !=9) #this corresponds to soy block 3, which is really borked on this day (adds a silly amount of variability, unlike block 1 and 2)
dat_cloudy_et = as.data.frame(dat_cloudy_et)
dat_cloudy_et =droplevels(dat_cloudy_et)

# add ar(1)
fit_cloudy_et_full = lme(lamet.ave ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corAR1(),
            control = ctrl,
            data=dat_cloudy_et)
```

```{r}
dat_cloudy_et_full_res = dat_cloudy_et%>%
  mutate(res=residuals(fit_cloudy_et_full, type="normalized"))%>%
  mutate(pred=predict(fit_cloudy_et_full))  

plot_cloudy_full = ggplot(data=dat_cloudy_et_full_res, aes(x=t, y=res, color=treatment))
plot_cloudy_full = plot_cloudy_full +geom_point()+ ggtitle("Normalized residuals (Lamet cloudy full model)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_cloudy_full = plot_cloudy_full + scale_x_continuous(breaks=seq(0,24,1))
plot_cloudy_full
hist(residuals(fit_cloudy_et_full, type="normalized"))
qqnorm(residuals(fit_cloudy_et_full, type="normalized"))
qqline(residuals(fit_cloudy_et_full, type="normalized"))
```

```{r, fig.cap="Cloudy day lamet estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_cloudy_lamet = as.data.frame(emmeans(fit_cloudy_et_full, ~ treatment*t_fac))
means_cloudy_lamet$t_fac = as.numeric(as.character(means_cloudy_lamet$t_fac))


plot_cloudy_lamet = ggplot(data=means_cloudy_lamet, aes(x=t_fac, y=emmean, color=treatment))
plot_cloudy_lamet = plot_cloudy_lamet + geom_point()+ xlab("Time Point (Hour)") + ylab("Lamet")
plot_cloudy_lamet = plot_cloudy_lamet + scale_x_continuous(breaks=seq(0,24,1))
plot_cloudy_lamet = plot_cloudy_lamet + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_cloudy_lamet
```

\pagebreak

### H

```{r, cache=T}
dat_cloudy_h = dat_cloudy#%>%
  # filter(id !=9)
dat_cloudy_h = as.data.frame(dat_cloudy_h)


fit_cloudy_H_full = lme(h ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corARMA(p=1),
            control = ctrl,
            data=dat_cloudy_h)
```

```{r}
dat_cloudy_H_full_res = dat_cloudy_h%>%
  mutate(res=residuals(fit_cloudy_H_full, type="normalized"))%>%
  mutate(pred=predict(fit_cloudy_H_full))

plot_cloudy_full = ggplot(data=dat_cloudy_H_full_res, aes(x=t, y=res, color=treatment))
plot_cloudy_full = plot_cloudy_full +geom_point()+ ggtitle("Normalized residuals (H cloudy full model)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_cloudy_full = plot_cloudy_full + scale_x_continuous(breaks=seq(0,24,1))
plot_cloudy_full
hist(residuals(fit_cloudy_H_full, type="normalized"))
qqnorm(residuals(fit_cloudy_H_full, type="normalized"))
qqline(residuals(fit_cloudy_H_full, type="normalized"))
```


```{r, fig.cap="cloudy day H estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_h = as.data.frame(emmeans(fit_cloudy_H_full, ~ treatment*t_fac))
means_h$t_fac = as.numeric(as.character(means_h$t_fac))

plot_h = ggplot(data=means_h, aes(x=t_fac, y=emmean, color=treatment))
plot_h = plot_h + geom_point()+ xlab("Time Point (Hour)") + ylab("H")
plot_h = plot_h + scale_x_continuous(breaks=seq(0,24,1))
plot_h = plot_h + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_h
```

\pagebreak

### $G_0$

```{r, cache=T}
dat_cloudy_g0 = dat_cloudy%>%
  filter(id %in% c(1, 2, 4, 6, 8, 9))
dat_cloudy_g0 = as.data.frame(dat_cloudy_g0)

fit_cloudy_G0_full = lme(g0 ~ treatment*t_fac,
            random = ~ 1 | block/id,
            weights = varComb(varIdent(form= ~ 1 | treatment),varIdent(form= ~ 1 | t_fac)),
            correlation = corAR1(),
            control = ctrl,
            data=dat_cloudy_g0)
```

```{r}
dat_cloudy_G0_full_res = dat_cloudy_g0%>%
  mutate(res=residuals(fit_cloudy_G0_full, type="normalized"))%>%
  mutate(pred=predict(fit_cloudy_G0_full))  

plot_cloudy_full = ggplot(data=dat_cloudy_G0_full_res, aes(x=t, y=res, color=treatment))
plot_cloudy_full = plot_cloudy_full +geom_point()+ ggtitle("Normalized residuals (G0 cloudy full model)") +xlab("Time Point (Hour)") + ylab("Normalized residuals")
plot_cloudy_full = plot_cloudy_full + scale_x_continuous(breaks=seq(0,24,1))
plot_cloudy_full
hist(residuals(fit_cloudy_G0_full, type="normalized"))
qqnorm(residuals(fit_cloudy_G0_full, type="normalized"))
qqline(residuals(fit_cloudy_G0_full, type="normalized"))
```


```{r, fig.cap= "Cloudy day G0 estimates and 95% CI. Note that the CI vaires by time and treatment, which is representative of the data."}
means_g0 = as.data.frame(emmeans(fit_cloudy_G0_full, ~ treatment*t_fac))
means_g0$t_fac = as.numeric(as.character(means_g0$t_fac))

plot_g0 = ggplot(data=means_g0, aes(x=t_fac, y=emmean, color=treatment))
plot_g0 = plot_g0 + geom_point()+ xlab("Time Point (Hour)") + ylab("G0")
plot_g0 = plot_g0 + scale_x_continuous(breaks=seq(0,24,1))
plot_g0 = plot_g0 + geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE))
plot_g0
```

\pagebreak

### $R_n$

$R_n$ isn't replicated over by treatment, there are no statistics required here.

```{r}
ggplot(dat_cloudy) +
 aes(x = t, y = rn, colour = treatment) +
 geom_point(size = 1L) +
 scale_color_hue() +
 theme_minimal()
```


# Averaged diurnal differences between Corn and IC (fig 3 from Bernacchi 2003)



# Daily $\lambda ET$ (fig 7 from Bernacchi 2003)